\documentclass[12pt]{article}

\input{packages}
\input{macros}

\begin{document}

    \begin{center}
        \section*{David Daniels}
        \cite{github}\href{https://github.com/tetricz}{Github} DavidLeeDaniels@pm.me - (281) 475-7897
    \end{center}

    \subsection*{Education}
    \begin{itemize}[leftmargin=0em]
        \item[] Masters of Computing Science \hfill Expected Spring 2025 \\
        Simon Fraser University
        \item[] Bachelor of Science in Computer Science \hfill 2023 \\
        University of Houston
        \item[] Associate of Science in Computer Science \hfill 2021 \\
        Lonestar College System
    \end{itemize}

    \subsection*{Research Interests}
    I am interested in pursuing unique ideas with the intentions to further improve the ways we 
    develop software for the future. Improving software systems and finding new development 
    methods to maintain security and efficiency.

    \subsection*{Papers}

    \cite{Amoozadeh_2023} Trust in Generative AI among students: An Exploratory Study
    
    \subsection*{Experience}
    \begin{itemize}[leftmargin=0em]
        \item[] \textbf{Graduate Reseach Assistant at Simon Fraser University \hfill Sept. 2023-Present} \\
        Literature review of existing research on program repair.

        \item[] \textbf{Undergraduate Researcher at University of Houston \hfill Sept. 2022-Sept. 2023} \\
        Setup Kubernetes cluster to run Anubis LMS for future infrastructure.
        Create a comprehensive Qualtrics survey to collect preliminary information.
        Quantitative and qualitative analysis of survey data.

        \item[] \textbf{Teaching Assistant at University of Houston \hfill Jan.  2023-May. 2023} \\
        Grade course assessments and provide feedback to ensure students understood the material.
        Hold office hours at varying times to ensure students have an opportunity to ask questions.
        Assist in answering student questions.\\
        Required skilled knowledge of C++ and Python.\\
        Create and utilize custom program analyses.\\
        Required knowledge of compiler design and implementation.

        \item[] \textbf{General Warehouse Hand at Aztec Events and Tents \hfill Sept. 2017-Mar.2019} \\
        Conduct thorough inspections of returned orders to assess damage, utilizing a keen eye for detail.
        Prepare and sanitize orders for next-day delivery.
        Successfully manage day-to-day operations of a small-scale warehouse, including supervising loading teams to ensure the quality of services provided.
    \end{itemize}


    \bibliographystyle{plain}
    \bibliography{david}

\end{document}
